SDG contributions

### 2023-09-15 article/article.qmd
add code about gender

```{r sdg_who_ptop_productivity_share_w_baseline, fig.asp=.5, fig.width=8}
pdata %>%
  plot_proportions(indicator = P_top10, n_frac_papers) +
  geom_line(data = baseline_data, linetype = 2, alpha = .7) +
  labs(y = "% of publications (fractional)", colour = expression(P["top 10%"]))
```

>>>>

```{r sdg_who_ptop_productivity_share_w_baseline, fig.asp=.5, fig.width=8}
pdata %>%
  plot_proportions(indicator = P_top10, n_frac_papers) +
  geom_line(data = baseline_data, linetype = 2, alpha = .7) +
  labs(y = "% of publications (fractional)", colour = expression(P["top 10%"]))
```
# Gender
Computations for gender could not be reproduced in the current repository 
because the data are unavailable.
The original gender-assignments were lost due to a prior server
becoming defunct. However, since the code for all other computations was fully
reproducible after setting up anew on a new server, I expect the results to be
reproducible in principle, if the data were available. The code below is 
provided for illustration, but was not run recently.

```{r, eval=FALSE}
gender_base <- papers %>% 
  select(paperid, SDG_label, year, is_oa) %>% 
  left_join(author_paper_affiliations_w_groups) %>% 
  left_join(author_metadata) %>% 
  select(paperid, SDG_label, year, author_position, authorid, 
         paper_author_cat, gender) %>% 
  filter(gender != "unknown", year < 2020)

gender_years <- gender_base %>% 
  group_by(SDG_label, year) %>% 
  count(gender) %>% 
  mutate(prop = n/sum(n)) %>% 
  collect()

gender_position <- gender_base %>% 
  group_by(SDG_label, year, author_position) %>% 
  count(gender) %>% 
  mutate(prop = n/sum(n)) %>% 
  collect()
```

```{r, eval=FALSE, fig.width=6, fig.height=3}
# Share of female authorships by SDG.
date_scale <- scale_x_date(breaks = as_year(c(2006, 2010, 2015, 2019)),
               date_labels = "%Y")
p <- gender_years %>% 
  filter(gender == "female") %>% 
  ggplot(aes(as_year(year), prop, colour = fix_sdg(SDG_label))) +
  geom_line() +
  geom_point() +
  date_scale +
  scale_y_continuous(labels = function(x) scales::percent(x, 1)) +
  colorspace::scale_color_discrete_qualitative() +
  labs(x = NULL, y = "Share of female authorships", colour = NULL) +
  theme(legend.position = "top")
p
```

```{r eval=FALSE, fig.width=8, fig.height=4}
# Share of women authorships by SDG and author position.
p <- gender_position %>% 
  filter(gender == "female") %>% 
  ggplot(aes(as_year(year), prop, colour = fix_sdg(SDG_label))) +
  geom_line() +
  geom_point() +
  date_scale +
  facet_wrap(vars(author_position)) +
  scale_y_continuous(labels = function(x) scales::percent(x, 1)) +
  colorspace::scale_color_discrete_qualitative() +
  labs(x = NULL, y = "Share of female authorships", colour = NULL) +
  theme(legend.position = "top")
p
```

# Open Access
